#
<p class="title2">
  Variant - Drug association clinical report<br />
  Date: `r format(Sys.Date(), "%d %B %Y")`
</p>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, comment = NA)
  source("variantAnnotation.R")
  # source(paste0(INSTALL_DIR,"/bin/tableMakeover.R"))
```

<p class="subheader">
  Analysis ID: `r analysisId`<br />
  Sample Name:  `r sample_name`<br />
  Sample ID: `r sampleId`<br />
  Total Variants: `r totalVariants`<br />
</p>

<link rel="stylesheet" href="https://use.fontawesome.com/releases/v5.7.0/css/all.css">

<h1>
<i class="fas fa-list-ul" style='font-size:28px'>
</i>
Clinically Actionable Variants list
</h1>


<p class="comment">
**actionableVariants** variant annotations of the `r totalVariants` variants called in the analysis were deemed clinically actionable and are reported below.
</p>
```{r actionable_variants, echo=FALSE}
kable(SNV[,c(1:4,6)]) %>%
  kable_styling(full_width = TRUE) %>%
  row_spec(0, bold = T, font_size = "10", align = "left", background = "#ffffff !important", color = "#248f8f !important")
```
